LAGOS lake depth

### 2021-08-10 figures/00_maps.Rmd
linting

gg_states <- 
  ggplot() + 
    geom_sf(data = study_bbox[1,], alpha = 1, size = 0.6, 
          color = "black", fill = "#1D9DCF") +
    geom_sf(data = states_all, fill = "gray", color = "black", size = 0.3) +
  # geom_sf(data = outline, color = "black", alpha = 0, size = 0.8) +
  # geom_sf(data = hu4, fill = "grey") +
    geom_sf(data = states_focal, fill = "white", color = "black", size = 0.4) + 
    geom_point_rast(data = dt_notsf, aes(x = X, y = Y, color = maxdepth_class), 
                    alpha = 0) +
    scale_color_manual(values = viridisLite::viridis(5)) +
    geom_point_rast(data = dplyr::filter(dt_notsf, lake_maxdepth_m < 10), 
            aes(x = X, y = Y, color = maxdepth_class), size = 0.2, alpha = 0.8) +
    geom_point_rast(data = dplyr::filter(dt_notsf, lake_maxdepth_m > 10), 
            aes(x = X, y = Y, color = maxdepth_class), size = 0.2, alpha = 0.8) +
    labs(color = "Max depth (m)") +
    coord_sf(datum =  NA) +
    theme_void()

@@

us_states <-dplyr::filter(
    dplyr::select(states_all, postal, iso_a2), iso_a2 == "US")
dt_plot <- dt %>%
  distinct(lagoslakeid, .keep_all = TRUE) %>%
  dplyr::filter(lake_waterarea_ha >= 4) %>%
  group_by(lake_state) %>%
  summarize(prop_maxdepth = mean(!is.na(lake_maxdepth_m))) %>%
  arrange(desc(prop_maxdepth))
dt_plot <- dt_plot %>%
  left_join(us_states, by = c("lake_state" = "postal")) %>%
  dplyr::filter(!is.na(prop_maxdepth)) %>%
  distinct(lake_state, .keep_all = TRUE)
st_geometry(dt_plot) <- dt_plot$geom

>>>>

gg_states <-
  ggplot() +
  geom_sf(data = study_bbox[1, ], alpha = 1, size = 0.6,
    color = "black", fill = "#1D9DCF") +
  geom_sf(data = states_all, fill = "gray", color = "black", size = 0.3) +
  # geom_sf(data = outline, color = "black", alpha = 0, size = 0.8) +
  # geom_sf(data = hu4, fill = "grey") +
  geom_sf(data = states_focal, fill = "white", color = "black", size = 0.4) +
  geom_point_rast(data = dt_notsf, aes(x = X, y = Y, color = maxdepth_class),
    alpha = 0) +
  scale_color_manual(values = viridisLite::viridis(5)) +
  geom_point_rast(data = dplyr::filter(dt_notsf, lake_maxdepth_m < 10),
    aes(x = X, y = Y, color = maxdepth_class), size = 0.2, alpha = 0.8) +
  geom_point_rast(data = dplyr::filter(dt_notsf, lake_maxdepth_m > 10),
    aes(x = X, y = Y, color = maxdepth_class), size = 0.2, alpha = 0.8) +
  labs(color = "Max depth (m)") +
  coord_sf(datum =  NA) +
  theme_void()

@@

us_states <- dplyr::filter(
  dplyr::select(states_all, postal, iso_a2), iso_a2 == "US")
dt_plot <- dt %>%
  distinct(lagoslakeid, .keep_all = TRUE) %>%
  dplyr::filter(lake_waterarea_ha >= 4) %>%
  group_by(lake_state) %>%
  summarize(prop_maxdepth = mean(!is.na(lake_maxdepth_m))) %>%
  arrange(desc(prop_maxdepth))
dt_plot <- dt_plot %>%
  left_join(us_states, by = c("lake_state" = "postal")) %>%
  dplyr::filter(!is.na(prop_maxdepth)) %>%
  distinct(lake_state, .keep_all = TRUE)
st_geometry(dt_plot) <- dt_plot$geom
